%        File: index.tex
%     Created: Fri Oct 23 03:00 PM 2020 +0
% Last Change: Fri Oct 23 03:00 PM 2020 +0
%
\documentclass[a4paper, 11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
\usepackage[super]{cite}
\bibliographystyle{ieeetr}
\usepackage[]{amsmath}
\numberwithin{equation}{subsection}
\usepackage{xcolor}
\usepackage[]{graphicx}
% color for general purposes
\definecolor{salmon}{RGB}{250, 128, 114}
\definecolor{grey}{RGB}{97, 97, 97}
\definecolor{bluegrey}{RGB}{96, 125, 139}
\definecolor{darkorange}{RGB}{245, 124, 0}
%color for listing block aka coding block
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{codebackground}{rgb}{0.95,0.95,0.92}
\definecolor{codeterminalbackground}{rgb}{0.95,0.95,0.95}
\setlength{\parindent}{0em}

\usepackage{listings}
\lstdefinestyle{python}{
	backgroundcolor=\color{codebackground},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=4
}
\lstdefinestyle{terminal}{
	backgroundcolor=\color{codeterminalbackground},
	stringstyle=\color{black},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=4,
	numbers=none
}
\lstset{language=Python, style=python}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true, 
	linkcolor=grey, 
	filecolor=grey,      
	urlcolor=bluegrey,
}

\title{Multiprocessing vs. threading in python\\
kinds of a lecture note for my reminder}
\author{Ziang Zhang \\ \texttt{ziang.zhang@kaust.edu.sa}}
\date{\today}


\begin{document}
\maketitle
\tableofcontents

My spider program with scipy encountered a problem. I have to wait for the downloading complete rather than start another spider job immediately. The multi processing or threading codes must be added to suit my need. Actually I have leart these contents multiple times but I keep forgetting. Here is the note of the new learning and hopefully I can keep the following knowledge in mind for longer time.

\section{Difference between process and thread}

    The first thing to make clear is the difference of process and thread. 

    \subsection{Process}

    Process means any program is in execution. A process can create other processes which are known as \textbf{Child processes}. Process takes more time to terminate and it is isolated means it does share memory with other processes. 
\newpage
%\bibliography{references}
\end{document}

